---
title: "R code for testing species-energy-area relationships in Merida, Mexico."
execute: 
  include: false
  message: false
  warning: false
format:
  html:
    toc: true
    toc-location: left-body
    toc-title: Contents
    embed-resources: true
    code-overflow: wrap
    self-contained: true
    grid:
      sidebar-width: 200px
      body-width: 1200px
      margin-width: 0px
      gutter-width: 1.5rem
editor: visual
---

Load packages

```{r}
#| label: load packages
#| eval: true

library(pacman)

p_load(brms, tidyverse, tidybayes, readr, sf, terra, lubridate,
       viridis, bayesplot, scales, marginaleffects, glue,
       kableExtra)

```

```{r}
#| label: import and organize bird data
#| eval: true

# Import data

all_birds <-
  list.files(path = "./Data", pattern = "\\.csv$") %>%
  map_df()

# Indicate if birds identified to genus or species level

all_birds <- all_birds %>%
  mutate(Level = ifelse(grepl("\\<sp\\>", Cientifico),
    "Genus", ifelse(grepl("\\<sp.\\>", Cientifico),
      "Genus", "Species"
    )
  )) %>%
  mutate(
    Ingles = ifelse(Level == "Genus", NA, Ingles),
    Español = ifelse(Level == "Genus", NA, Español)
  ) %>%
  mutate(Date = as.Date(as.character(Fecha), format = "%Y%m%d")) %>%
  mutate(
    Ingles = str_to_title(Ingles),
    Español = str_to_title(Español)
  )

# Discover whether there are multiple spellings of english and spanish names

all_birds <- all_birds %>%
  group_by(Cientifico) %>%
  nest() %>%
  mutate(
    Eng_dbl = map(data, ~ length(unique(.$Ingles))),
    Span_dbl = map(data, ~ length(unique(.$Español))),
    AOU_dbl = map(data, ~ length(unique(.$AOU)))
  ) %>%
  unnest(c(data, Eng_dbl, Span_dbl, AOU_dble)) %>%
  mutate(
    Misspelled_eng = ifelse(Eng_dbl > 1, "Yes", "No"),
    Misspelled_span = ifelse(Span_dbl > 1, "Yes", "No"),
    Misspelled_aou = ifelse(AOU_dbl > 1, "Yes", "No"),
  )

# write.csv(all_birds, "all_birds.csv",
#          fileEncoding = "latin1", row.names = FALSE)

# Re-import to check only one english and spanish name and aou per scientific name

all_birds <- read_csv("all_birds.csv",
  locale = locale(encoding = "latin1")
) %>%
  group_by(Cientifico) %>%
  nest() %>%
  mutate(
    Eng_dbl = map(data, ~ length(unique(.$Ingles))),
    Span_dbl = map(data, ~ length(unique(.$Español))),
    AOU_dbl = map(data, ~ length(unique(.$AOU)))
  ) %>%
  unnest(c(Eng_dbl, Span_dbl, AOU_dbl))

all_birds %>%
  ungroup() %>%
  filter(Eng_dbl > 1)

all_birds %>%
  ungroup() %>%
  filter(Span_dbl > 1)

all_birds %>%
  ungroup() %>%
  filter(AOU_dbl > 1)

# Remove higher level identifications if a species was recorded in the same site/date

all_birds_2 <- all_birds %>%
  select(-Eng_dbl, -Span_dbl, -AOU_dbl) %>%
  unnest(data) %>%
  select(
    -Fecha, -Eng_dbl, -Span_dbl, #-AOU_dbl, 
    -Misspelled_eng, -Misspelled_span, #-Misspelled_AOU
  ) %>%
  rowwise() %>%
  mutate(Genus = word(Cientifico)) %>%
  ungroup() %>%
  distinct(Sitio, Date, Genus, .keep_all = TRUE) %>%
  rowwise() %>%
  mutate(Family = ifelse(grepl("Swallow", Ingles), "Hirundinidae",
    ifelse(Cientifico == "Hirundinidae", "Hirundinidae",
      ifelse(grepl("Hummingbird", Ingles), "Trochilidae",
        ifelse(Cientifico == "Trochilidae",
          "Trochilidae", Cientifico
        )
      )
    )
  )) %>%
  ungroup() %>%
  distinct(Sitio, Date, Family, .keep_all = TRUE) %>%
  select(Sitio, Date, Cientifico, Ingles, Español, AOU, Visuales, Level) %>%
  rename(
    Site = Sitio, Scientific_name = Cientifico, English_name = Ingles,
    Spanish_name = Español, Count = Visuales
  )
```

```{r}
#| label: summarize abundance per species per site
#| eval: true 

species_types <- read_csv(".Data/species_types.csv",
  locale = locale(encoding = "latin1")
)

bird_abundances <- all_birds_2 %>%
  group_by(Site, Scientific_name, English_name, Spanish_name, AOU) %>%
  summarize(Abundance = sum(Count, na.rm = T)) %>%
  left_join(., species_types, by = "Scientific_name") %>%
  ungroup() %>%
  select(Site, 
         Scientific_corrected, 
         English_name.y, 
         Spanish_name.y, 
         Status, 
         Habitat, 
         Abundance)

abundance_table <- bird_abundances %>%
  ungroup() %>%
  arrange(Scientific_corrected) %>%
  pivot_wider(
    names_from = Site,
    values_from = Abundance,
    values_fill = 0
  ) %>%
  select(
    Scientific_corrected,
    English_name.y,
    Spanish_name.y,
    Acuaparque,
    Fracc,
    JBR,
    Kai_Luum,
    Mapsa,
    PAEP,
    PEP,
    Habitat,
    Status
  ) %>%
  rename(
    "Scientific name" = Scientific_corrected,
    "English name" = English_name.y,
    "Spanish name" = Spanish_name.y,
    "Fraccionamiento del Parque" = Fracc,
    "Jardín Botánico Roger Orellana" = JBR,
    "Kai Luum" = Kai_Luum,
    "Parque Eco Arqueológico de Xoclán" = PAEP,
    "Parque Ecológico Del Poniente" = PEP
  ) %>%
  kable("html",
    caption = glue("<span style='font-size:12pt;'>Table S1. Species abundances summed across all samples from March 2, 2016 to August 23, 2018 for each of seven green areas in Merida, Yucatan, Mexico .</span>")
  ) %>%
  kable_styling(
    full_width = TRUE,
    bootstrap_options = "none",
    font_size = 10,
    position = "left"
  ) %>% 
  #row_spec(0, 
  #         angle = -45,
  #         extra_css = "border-bottom: 1em solid white; padding-bottom: 1em;") %>% 
  column_spec(4:12, width = "2cm", extra_css = "padding-right: 2em;") %>%
  #scroll_box(width = "7in") %>%
  save_kable("Table_S1.html")
```

```{r}
#| label: calculate species richness
#| eval: true 

bird_richness_summary <- all_birds_2 %>%
  left_join(., species_types, by = "Scientific_name") %>%
  ungroup() %>%
  select(Site, Scientific_corrected, English_name.y, Spanish_name.y, Status, Habitat) %>%
  group_by(Habitat, Status) %>%
  summarize(Richness = n_distinct(Scientific_corrected))
  
bird_richness <- all_birds_2 %>%
  left_join(., species_types, by = "Scientific_name") %>%
  ungroup() %>%
  select(Site, Date, Scientific_corrected, English_name.y, Spanish_name.y, Status, Habitat, Count) %>%
  rename(Scientific_name = Scientific_corrected, English_name = English_name.y, 
         Spanish_name = Spanish_name.y) %>%
  mutate(Flyover = ifelse(
    (grepl("Swift", English_name)|grepl("Swallow", English_name)|grepl("Vulture", English_name))&
      is.na(Count), "Flyover", "Keep")) %>%
  filter(Flyover == "Keep", Habitat == "Terrestrial") %>%
  group_by(Site, Date, Status) %>%
  summarize(Richness = n_distinct(Scientific_name)) %>%
  ungroup() %>%
  mutate(Date = as.Date(Date, format = "%m/%d/%Y")) 

```

```{r}
#| label: explore species richness
#| eval: true 

bird_richness %>%
  ggplot(aes(x = Richness)) +
  geom_histogram(fill = "orange") +
  facet_grid(Status ~ .) +
  theme_classic()

```

```{r}
#| label: import park shape files
#| eval: true

sites <- st_read("data/Merida_parks.shp")

```

```{r}
#| label: import landsat
#| eval: true

red_landsat <- rast(list.files("Landsat", pattern = "B4.TIF$", full.names = TRUE))

```

Add NDVI and area variables

April - August, 2016 = 2015-2016 September - December, 2016 = 2016-2017 January - August, 2017 = 2016-2017 September - December, 2017 = 2017-2018 January - August, 2018 = 2017-2018

20160410 APRIL 2015-2016 20160523 MAY 2015-2016 20161007 OCT 2016-2017 --\> Code to Sep/Oct 20161106 NOV 2016-2017 20161206 DEC 2016-2017 20170125 JAN 2016-2017 20170224 FEB 2016-2017 20170405 APR 2016-2017 --\> Code to Mar/Apr 20170515 MAY 2016-2017 20170912 SEP 2017-2018 --\> Code to Sep/Oct 20171226 DEC 2017-2018 20180110 JAN 2017-2018 20180219 FEB 2017-2018 20180326 MAR 2017-2018 --\> Code to Mar/Apr

```{r}

ndvi_data <- dir_ls(paste0(getwd(), "/Gerardo_data2024/NDVI_values"), glob = "*.csv") %>%
  set_names(\(x) path_ext_remove(path_file(x))) %>%
  map(read.csv) %>%
  list_rbind(names_to = "File") %>%
  select(-c(X, ID, cell)) %>%
  pivot_longer(-c(File, Sitio), names_to = "Date_bad", values_to = "NDVI") %>%
  filter(!is.na(NDVI)) %>%
  mutate(Date = as.Date(str_remove(File, "NDVI_"), format = "%Y%m%d")) %>%
  select(-File, -Date_bad) %>%
  rename(Site = Sitio) %>%
  group_by(Site, Date) %>%
  summarize(ndvi = mean(NDVI))

enviro_data <- read_csv("ndvi_area_migratorias.csv") %>%
  select(Sitio, A_VEG) %>%
  distinct() %>%
  rename(Site = Sitio, Area = A_VEG) %>%
  right_join(., ndvi_data, by = "Site")

data_all <- full_join(bird_richness %>%
                        rename(Date_bird = Date),
                      enviro_data, by = "Site", relationship = "many-to-many") %>%
  mutate(Date_diff = abs(Date_bird - Date)) %>%
  group_by(Site, Date, Status) %>%
  slice_min(Date_diff) %>%
  mutate(Remove = ifelse(Site == "Acuaparque"&Date<"2016-07-19", "Yes", 
                         ifelse(Site == "Fracc"&Date<"2016-07-19", "Yes", "No"))) %>%
  mutate(Month = as.numeric(format(Date, "%m")),
         Year = as.numeric(format(Date, "%Y"))) %>%
  filter(Month >= 9|Month <= 5,
         Remove == "No") 
  
  
  %>%
  mutate(Day_difference = abs(Survey_day - Map_day)) %>%
  group_by(Site, Status, Month, Year) %>%
  filter(Day_difference == min(Day_difference)) #%>% ## CHECK MONTHS AND YEARS
  group_by(Site, Month, Year, NDVI, AREA, Status) %>%
  summarize(Richness = max(Richness), NDVI = max(NDVI), AREA = max(AREA))
  
  

#%>%
  select(Site, Survey, Richness, NDVI, AREA, Type)%>%
  mutate(Year = as.numeric(substring(Survey, 1, 4)), 
         Month = as.numeric(substring(Survey, 5, 6))) %>%
  mutate(Year_2 = ifelse(Year == 2016 & Month <= 8, "2015-2016", 
                         ifelse(Year == 2016 & Month > 8, "2016-2017", 
                                ifelse(Year == 2017 & Month <= 8, "2016-2017", 
                                       "2017-2018")))) %>%
  mutate(Month_2 = case_when(Month == 1 ~ "January",
                             Month == 2 ~ "February",
                             Month == 3 ~ "March",
                             Month == 4 ~ "April",
                             Month == 5 ~ "May",
                             Month == 9 ~ "September",
                             Month == 10 ~ "October",
                             Month == 11 ~ "November",
                             Month == 12 ~ "December")) %>%
  bind_rows(., data_residents %>%
              filter(Site == "JBR", Year_2 == "2016-2017", Month_2 == "October") %>%
              mutate(Richness = 0, Type = "migrants")) ##JBR for October 2016-2017 is missing

```

Modeling and prediction functions

```{r}

# Function for model
stan_model<-function(x){

  stan_lmer(Richness.l ~ NDVI.l + AREA.l + (NDVI.l + AREA.l|Year_2/Month_2), 
      data = x,
      #init = 0, 
      iter = 5000, 
      warmup = 1000,
      adapt_delta = 0.99)
  
}

# Function for extracting coefficients

stan_coefficients <- function(x){
  
  fixed_effects <- x %>%
    gather_draws(`(Intercept)`, NDVI.l, AREA.l) %>%
    group_by(.variable) %>%
    median_hdi() %>%
    rename(term = .variable, Coefficient = .value) %>%
    mutate(group = "fixed") %>%
    select(term, group, Coefficient, .lower, .upper, .width, .point, .interval)
  
  
  random_effects <- x %>%
    spread_draws(NDVI.l, AREA.l, b[term, group]) %>%
    filter(term != "(Intercept)") %>%
    mutate(Coefficient = ifelse(term == "NDVI.l", b + NDVI.l, b + AREA.l)) %>%
    group_by(term, group) %>%
    median_hdi(Coefficient)
  
  bind_rows(fixed_effects, random_effects) %>%
    mutate(Parameter = case_when(term == "(Intercept)" ~ "Intercept",
                                 term == "NDVI.l" ~ "Energy",
                                 term == "AREA.l" ~ "Area"))
  
}

# Function to create new data for prediction

stan_prediction_data <- function(x){
  
  ndvi_range <- x %>%
    group_by(Month_2) %>%
    summarize(NDVI.min = min(NDVI.l),
              NDVI.max = max (NDVI.l)) %>%
    group_by(Month_2) %>%
    nest() %>%
    mutate(NDVI.l = map(data, ~seq(round(.$NDVI.min, 2), round(.$NDVI.max, 2), 0.01))) %>%
    unnest(NDVI.l) %>%
    select(-data)
  
  predicting_data <- left_join(x %>%
                                 select(AREA.l, Month_2, Year_2),
                               ndvi_range, 
                               by = "Month_2")
  
}
    
stan_predictions_na <- function(x, y){
  
    predictions_na <- y %>%
      select(NDVI.l, AREA.l) %>%
      distinct() %>%
      add_epred_draws(x, re_formula = NA) %>%
      group_by(NDVI.l, AREA.l) %>%
      median_qi(.epred) %>%
      rename(Richness = .epred, Lower = .lower, Upper = .upper) #%>%  
     # mutate(NDVI = exp(NDVI.l), AREA = exp(AREA.l))
      
}


stan_predictions_null <- function(x, y){
  
    predictions_null <- y %>%
      add_epred_draws(x, re_formula = NULL) %>%
      group_by(NDVI.l, AREA.l, Month_2, Year_2) %>%
      median_qi(.epred) %>%
      rename(Richness = .epred, Lower = .lower, Upper = .upper) #%>%  
      #mutate(NDVI = exp(NDVI.l), AREA = exp(AREA.l))
      
}
```

Load data

April - August, 2016 = 2015-2016 September - December, 2016 = 2016-2017 January - August, 2017 = 2016-2017 September - December, 2017 = 2017-2018 January - August, 2018 = 2017-2018

20160410 APRIL 2015-2016 20160523 MAY 2015-2016 20161007 OCT 2016-2017 --\> Code to Sep/Oct 20161106 NOV 2016-2017 20161206 DEC 2016-2017 20170125 JAN 2016-2017 20170224 FEB 2016-2017 20170405 APR 2016-2017 --\> Code to Mar/Apr 20170515 MAY 2016-2017 20170912 SEP 2017-2018 --\> Code to Sep/Oct 20171226 DEC 2017-2018 20180110 JAN 2017-2018 20180219 FEB 2017-2018 20180326 MAR 2017-2018 --\> Code to Mar/Apr

```{r}

data_residents <- read_csv("ndvi_area_residentes.csv") %>%
  mutate(Type = "residents", Survey = as.character(Semana_mapa)) %>%
  rename(Site = Sitio, Richness = Riqueza_aves) %>%
  select(Site, Survey, Richness, NDVI, AREA, Type) %>%
  mutate(Year = as.numeric(substring(Survey, 1, 4)), 
         Month = as.numeric(substring(Survey, 5, 6))) %>%
  mutate(Year_2 = ifelse(Year == 2016 & Month <= 8, "2015-2016", 
                         ifelse(Year == 2016 & Month > 8, "2016-2017", 
                                ifelse(Year == 2017 & Month <= 8, "2016-2017", 
                                       "2017-2018")))) %>%
  mutate(Month_2 = case_when(Month == 1 ~ "January",
                             Month == 2 ~ "February",
                             Month == 3 ~ "March",
                             Month == 4 ~ "April",
                             Month == 5 ~ "May",
                             Month == 6 ~ "June",
                             Month == 7 ~ "July",
                             Month == 8 ~ "August",
                             Month == 9 ~ "September",
                             Month == 10 ~ "October",
                             Month == 11 ~ "November",
                             Month == 12 ~ "December")) %>%
  filter(!Month %in% c(6,7,8))
         
      

data_migrants <- read_csv("ndvi_area_migratorias.csv") %>%
  mutate(Type = "migrants", Survey = as.character(Semana_mapa)) %>%
  rename(Site = Sitio, Richness = Riqueza_aves) %>%
  select(Site, Survey, Richness, NDVI, AREA, Type)%>%
  mutate(Year = as.numeric(substring(Survey, 1, 4)), 
         Month = as.numeric(substring(Survey, 5, 6))) %>%
  mutate(Year_2 = ifelse(Year == 2016 & Month <= 8, "2015-2016", 
                         ifelse(Year == 2016 & Month > 8, "2016-2017", 
                                ifelse(Year == 2017 & Month <= 8, "2016-2017", 
                                       "2017-2018")))) %>%
  mutate(Month_2 = case_when(Month == 1 ~ "January",
                             Month == 2 ~ "February",
                             Month == 3 ~ "March",
                             Month == 4 ~ "April",
                             Month == 5 ~ "May",
                             Month == 9 ~ "September",
                             Month == 10 ~ "October",
                             Month == 11 ~ "November",
                             Month == 12 ~ "December")) %>%
  bind_rows(., data_residents %>%
              filter(Site == "JBR", Year_2 == "2016-2017", Month_2 == "October") %>%
              mutate(Richness = 0, Type = "migrants")) ##JBR for October 2016-2017 is missing

data_all <- bind_rows(data_residents, data_migrants) %>%
  mutate(Richness.l = log10(Richness + 1),
         NDVI.l = log10(NDVI),
         AREA.l = log10(AREA))

data_reduced <- data_all %>%
  mutate(Month_2 = case_when(Month_2 == "September" ~ "September/October",
                             Month_2 == "October" ~ "September/October",
                             Month_2 == "March" ~ "March/April",
                             Month_2 == "April" ~ "March/April",
                             .default = as.character(Month_2)))
```

Run models

```{r}
stan_results <- data_reduced %>%
  group_by(Type) %>%
  nest() %>%
  mutate(Model = map(data, stan_model)) %>%
  mutate(Model_estimates = map(Model, stan_coefficients)) %>%
  mutate(new_data = map(data, stan_prediction_data)) %>%  
  mutate(Predictions_na = map2(Model, new_data, stan_predictions_na),
         Predictions_null = map2(Model, new_data, stan_predictions_null))

save.image("Gerardo_analysis_Apr2023_nointeraction.RData")
```

Model diagnostics

```{r}

stan_diag <- stan_results %>%
  mutate(Posterior_check = map(Model, ~pp_check(.)),
         Trace = map(Model, ~mcmc_trace(., pars = c("(Intercept)",
                                                    "NDVI.l",
                                                    "AREA.l", 
                                                    "sigma"))),
         rhat = map(Model, ~mcmc_rhat(rhat(.))),
         neff = map(Model, ~mcmc_neff(neff_ratio(.)))) 

ggsave(ggarrange(plotlist = stan_diag$Posterior_check, ncol = 1, nrow = 2,
          widths = c(1, 1), 
          labels = c("Residents", "Migrants"),
          label.x = 0.05),
       filename = "ppcheck_plots.png",
       device="png",
       width=23.4,
       height=17.4,
       units="cm",
       dpi=600)

ggsave(ggarrange(plotlist = stan_diag$Trace, ncol = 1, nrow = 2,
          widths = c(1, 1), 
          labels = c("Residents", "Migrants"),
          label.x = 0.05),
       filename = "trace_plots.png",
       device="png",
       width=23.4,
       height=17.4,
       units="cm",
       dpi=600)

ggsave(ggarrange(plotlist = stan_diag$rhat, ncol = 1, nrow = 2,
          widths = c(1, 1), 
          labels = c("Residents", "Migrants"),
          label.x = 0.05),
       filename = "rhat_plots.png",
       device="png",
       width=23.4,
       height=17.4,
       units="cm",
       dpi=600)

ggsave(ggarrange(plotlist = stan_diag$neff, ncol = 1, nrow = 2,
          widths = c(1, 1), 
          labels = c("Residents", "Migrants"),
          label.x = 0.05),
       filename = "neff_plots.png",
       device="png",
       width=23.4,
       height=17.4,
       units="cm",
       dpi=600)


```

Summarize and graph results

```{r}

stan_estimates_figure <- stan_results %>%
  select(Type, Model_estimates) %>%
  unnest(Model_estimates) %>% 
  mutate(Parameter = factor(Parameter, levels = c("Intercept", "Energy", "Area"))) %>%
  filter(Parameter != "Intercept", group == "fixed") %>%
  ggplot(aes(x = Parameter, y = Coefficient, col = Type)) +  
  geom_point(size = 4, position = position_dodge(0.3)) +
  geom_errorbar(aes(ymin = .lower, ymax = .upper), size = 2, width = 0.2, 
                position = position_dodge(0.3)) +
  geom_hline(yintercept = 0, size = 2, linetype = 2, color = "grey") +
  scale_y_continuous(name = "\nParameter estimate") +
  scale_x_discrete(name="") + 
  scale_color_viridis_d(name = "", direction = -1) +
  theme_classic() + 
  theme(axis.line.x = element_line(colour="black"), 
        axis.line.y = element_line(colour="black"), 
        text = element_text(size = 12)) +
  coord_flip()

stan_estimates_figure

ggsave("Parameter_estimates.png", device="png", width=23.4, height=17.4, units="cm", dpi=300)

stan_estimates_month <- stan_results %>%
  select(Type, Model_estimates) %>%
  unnest(Model_estimates) %>% 
  mutate(Parameter = factor(Parameter, levels = c("Intercept", "Area", "Energy"))) %>%
  filter(Parameter != "Intercept", group != "fixed") %>%
  rowwise() %>%
  mutate(Month = str_split(group, ":")[[1]][3], Year = str_split(group, ":")[[1]][4]) %>%
  filter(!is.na(Month)) %>%
  mutate(Month = factor(Month, levels = c("May", "March/April", "February", 
                                           "January", "December", "November",
                                           "September/October"))) %>%
  filter(Year == "2016-2017") %>%
  ggplot(aes(x = Month, y = Coefficient, color = Type)) +  
  geom_point(size = 4, position = position_dodge(0.3)) +
  geom_errorbar(aes(ymin = .lower, ymax = .upper), size = 2, width = 0.2, 
                position = position_dodge(0.3)) +
  #geom_hline(yintercept = 0, size = 2, linetype = 2, color = "grey") +
  facet_grid(. ~ Parameter, scales = "free") + 
  scale_y_continuous(name = "\nParameter estimate") +
  scale_x_discrete(name="") + 
  scale_color_viridis_d(name = "", direction = -1) +
  theme_classic() + 
  theme(axis.line.x = element_line(colour="black"), 
        axis.line.y = element_line(colour="black"), 
        text = element_text(size = 12)) +
  coord_flip()

stan_estimates_month

ggsave("Parameter_estimates_monthly.png", device="png", 
       width=23.4, height=17.4, units="cm", dpi=300)

```

Figure of predictions

```{r}

stan_predictions_na_figure <- stan_results %>%
  ungroup() %>%
  select(Type, Predictions_na) %>%
  unnest(Predictions_na) %>%
  mutate(var_ndvi = "NDVI", var_area = "Area") %>% 
  pivot_longer(cols = c(var_ndvi, var_area), names_to = "Variable") %>%
  mutate(Keep = case_when(#value == "Area" & NDVI.l == min(.$NDVI.l) ~ "yes",
                          value == "Area" & NDVI.l == round(median(.$NDVI.l), 2) ~ "yes",
                          #value == "Area" & NDVI.l == max(.$NDVI.l) ~ "yes",
                          #value == "NDVI" & AREA.l == min(.$AREA.l) ~ "yes",
                          value == "NDVI" & AREA.l == median(.$AREA.l) ~ "yes",
                          #value == "NDVI" & AREA.l == max(.$AREA.l) ~ "yes",
                          .default = "no")) %>%
  filter(Keep == "yes") %>%
  mutate(X_var = ifelse(value == "NDVI", NDVI.l, AREA.l)) %>%
  #arrange(value, X_var) %>%
  #mutate(facet_str = rep(c("Min", "Median", "Max"), length.out = nrow(.))) %>%
  #mutate(facet_str = factor(facet_str, c("Min", "Median", "Max")),
  #       value = ifelse(value == "NDVI", "Energy", "Area")) %>%
  ggplot(aes(x = X_var, y = Richness)) +  
  geom_line(size = 2) +
  facet_grid(Type ~ value) +
  geom_ribbon(aes(ymin = Lower, 
                  ymax = Upper), 
              show.legend = FALSE, 
              color = NA,
              alpha = 0.3) +
  scale_y_continuous(name = "log(Species richness + 1)\n") +
  scale_x_continuous(name="\nlog(NDVI or Area)") + 
  theme_classic() + 
  theme(axis.line.x = element_line(colour="black"), 
        axis.line.y = element_line(colour="black"), 
        text = element_text(size = 12))

stan_predictions_na_figure

ggsave("Predictions_average.png", device="png", 
       width=23.4, height=17.4, units="cm", dpi=300)

stan_predictions_monthly_figure <- stan_results %>%
  ungroup() %>%
  select(Type, Predictions_null) %>%
  unnest(Predictions_null) %>%
  mutate(var_ndvi = "NDVI", var_area = "Area") %>% 
  pivot_longer(cols = c(var_ndvi, var_area), names_to = "Variable") %>%
  group_by(Type, Month_2, Year_2) %>%
  mutate(Median = round(median(NDVI.l), 2)) %>%
  mutate(Median_diff = NDVI.l - Median) %>%
  mutate(Keep = case_when(value == "Area" & round(Median_diff, 2) == 0 ~ "yes",
                          value == "NDVI" & AREA.l == median(AREA.l) ~ "yes",
                          .default = "no")) %>%
  filter(Keep == "yes") %>%
  mutate(X_var = ifelse(value == "NDVI", NDVI.l, AREA.l),
         facet_var = ifelse(value == "NDVI", AREA.l, NDVI.l)) %>%
  mutate(Month_2 = case_when(Month_2 == "September/October" ~ "Sep/Oct",
                             Month_2 == "November" ~ "Nov",
                             Month_2 == "December" ~ "Dec",
                             Month_2 == "January" ~ "Jan",
                             Month_2 == "February" ~ "Feb",
                             Month_2 == "March/April" ~ "Mar/Apr",
                             Month_2 == "May" ~ "May" )) %>%
  mutate(Month_3 = factor(Month_2, levels = c("Sep/Oct",
                                              "Nov",
                                              "Dec",
                                              "Jan", 
                                              "Feb",
                                              "Mar/Apr", 
                                              "May")),
         value = ifelse(value == "NDVI", "Energy", "Area")) %>%
  filter(Year_2 == "2016-2017") %>%
  ggplot(aes(x = X_var, y = Richness, color = Type)) +  
  geom_line(size = 2) +
  #facet_nested(Type + value ~ Month_3) +
  #facet_nested(Month_3 ~ value + Type, scales = "free_x") +
  facet_grid(Month_3 ~ value, scales = "free_x") +
  scale_color_grey() +
  geom_ribbon(aes(ymin = Lower, 
                  ymax = Upper), 
              show.legend = FALSE, 
              #color = NA,
              alpha = 0.3) +
  scale_y_continuous(name = "log(Species richness + 1)\n") +
  scale_x_continuous(name="\nlog(NDVI or Area)") + 
  
  theme_classic() + 
  theme(axis.line.x = element_line(colour="black"), 
        axis.line.y = element_line(colour="black"), 
        text = element_text(size = 12))
  
#stan_predictions_monthly_figure
  

ggsave("Predictions_monthly.png", device="png", 
       width=23.4, height=17.4, units="cm", dpi=300)


```

Actual area gradients across months

```{r}
parks_predictions <- stan_results %>%
  mutate(parks = map2(Model, data, stan_predictions_null))

stan_predictions_parks <- parks_predictions %>%
  ungroup() %>%
  select(Type, parks) %>%
  unnest(parks) %>%
  mutate(Month_2 = case_when(Month_2 == "September/October" ~ "Sep/Oct",
                             Month_2 == "November" ~ "Nov",
                             Month_2 == "December" ~ "Dec",
                             Month_2 == "January" ~ "Jan",
                             Month_2 == "February" ~ "Feb",
                             Month_2 == "March/April" ~ "Mar/Apr",
                             Month_2 == "May" ~ "May" )) %>%
  mutate(Month_3 = factor(Month_2, levels = c("Sep/Oct",
                                              "Nov",
                                              "Dec",
                                              "Jan", 
                                              "Feb",
                                              "Mar/Apr", 
                                              "May"))) %>%
  filter(Year_2 == "2016-2017") %>%
  ggplot(aes(x = AREA.l, y = Richness)) +  
  geom_line(size = 2) +
  #facet_nested(Type + value ~ Month_3) +
  facet_nested(Month_3 ~ Type, scales = "free_x") +
  geom_ribbon(aes(ymin = Lower, 
                  ymax = Upper), 
              show.legend = FALSE, 
              color = NA,
              alpha = 0.3) +
  scale_y_continuous(name = "log(Species richness + 1)\n") +
  scale_x_continuous(name="\nlog(Area)") + 
  theme_classic() + 
  theme(axis.line.x = element_line(colour="black"), 
        axis.line.y = element_line(colour="black"), 
        text = element_text(size = 12))
  
stan_predictions_parks
  

ggsave("Parks_monthly.png", device="png", 
       width=23.4, height=17.4, units="cm", dpi=300)
```

Priors

```{r}
Priors_used <- stan_results %>%
  filter(Type=="residents") %>%
  ungroup() %>%
  mutate(Priors = map(Model, ~prior_summary(.x))) %>%
  pluck("Priors")

Covariance <- stan_results %>%
  filter(Type=="residents") %>%
  ungroup() %>%
  mutate(Cov = map(Model, ~summary(.x))) %>%
  pluck("Cov")

```
